Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-23 paper/agree.tex
fiddling with contracts discussion
checkpointing. Re-org is done (for now). Mostly done describing AGREE contracts. Synthesis.tex merged with semantics.tex

This section gives an overview of AGREE's assume-guarantee reasoning
system, abstractly defining the verification conditions that AGREE
checks in order to establish overall system correctness at the model
level.  The discussion then becomes more concrete, showing how the
AGREE contract specification language is used to specify the
cyber-hardened system of \figref{fig:hardened}. It explains the the
top-level specification of the example system, then shifts to the
specifications for the filter and the monitor.  These two
specifications are those that are synthesized to equivalent CakeML by
SPLAT.

%% These conditions are useful in understanding how the semantics in
%% synthesis differ from those in the assume-guarantee reasoning
%% in \secref{sec:semantics}.

\subsection{Verification Conditions}
\input{verification-conditions}

\subsection{System Contract}
\input{sw-contract}

\subsection{Cyber-hardening the System Implementation}
\input{high-assurance-contracts}

>>>>

This section gives an abstract mathematical overview of AGREE's
compositional reasoning system, defining assume-guarantee contracts
and the verification conditions that AGREE checks in order to
modularly establish overall system correctness at the model level.
The syntax and semantics of AGREE are sketched in some detail.  The
discussion then becomes more concrete, showing---by example---how the
AGREE contract language is used to specify the cyber-hardened system
of \figref{fig:hardened}. The discussion proceeds from the
system-level contract to the filter and monitor components, which rely
on the notion of a \emph{code contract} to support code generation.

\subsection{Contracts and verification conditions}
\input{verification-conditions}

### 2022-03-23 paper/example.tex
checkpointing. Re-org is done (for now). Mostly done describing AGREE contracts. Synthesis.tex merged with semantics.tex

High-assurance components are automatically synthesized by SPLAT from
the AGREE specifications to equivalent programs in the CakeML
language.  The synthesis toolchain generates a proof that equates the
meaning of the AGREE specification to the behavior of the CakeML
program.  In other words, for any set of input streams that meet the
component's contract assumptions, the output streams produced from the
synthesized CakeML code exactly match those defined by the
high-assurance component's guarantees.  CakeML provides verified
compilation to binaries for several different platforms, meaning that
the resulting binaries exactly preserve the meaning of the original
CakeML code \cite{cakeml}.

>>>>

\subsection{Code synthesis}
High-assurance components are automatically synthesized by SPLAT from
the AGREE specifications to equivalent programs in the CakeML
language.  The synthesis toolchain generates a proof that equates the
meaning of the AGREE specification to the behavior of the CakeML
program.  In other words, for any set of input streams that meet the
component's contract assumptions, the output streams produced from the
synthesized CakeML code exactly match those defined by the
high-assurance component's guarantees.  CakeML provides verified
compilation to binaries for several different platforms, meaning that
the resulting binaries exactly preserve the meaning of the original
CakeML code \cite{cakeml}.

### 2022-03-23 paper/high-assurance-contracts.tex
checkpointing. Re-org is done (for now). Mostly done describing AGREE contracts. Synthesis.tex merged with semantics.tex

As previously discussed, transformations carried out in the BriefCASE
interface have created a cyber-hardened system, protecting against
malicious AI behavior, by inserting a high-assurance filter and
monitor between the AI and the WM (see \figref{fig:hardened}). The
filter protects the WM from malformed data and the monitor protects
the WM from (possibly malicious) spontaneous or delayed responses.
These components were added, one at a time, by
\begin{itemize}
  \item first, selecting the connection in the model where the
    component is to appear,
  \item second, choosing the appropriate transformation, and
  \item third, specifying the relevant filtering or monitoring \emph{policy} (behavior).
\end{itemize}

>>>>

As previously discussed, transformations carried out in the BriefCASE
interface have created a cyber-hardened system, protecting against
malicious AI behavior, by inserting a high-assurance filter and
monitor between the AI and the WM (see \figref{fig:hardened}). The
filter protects the WM from malformed data and the monitor protects
the WM from (possibly malicious) spontaneous or delayed responses.
These components were added, one at a time, by
\begin{enumerate}
  \item selecting the connection in the model where the
    component is to appear,
  \item choosing the appropriate transformation, and
  \item specifying the relevant filtering or monitoring \emph{policy} (behavior).
\end{enumerate}

### 2022-03-23 paper/paper.tex
moving things around; result is not entirely coherent
checkpointing. Re-org is done (for now). Mostly done describing AGREE contracts. Synthesis.tex merged with semantics.tex

\section{Assume-guarantee reasoning in AGREE}
\label{sec:agree}
\input{agree}

\subsection{Revisions}
\begin{compactitem}
  \item \sout{Add in the AGREE specification for the system}
  \item \sout{Add in the AGREE verification conditions (e.g., similar to those in the Scheduled Components NFM submission)}
  \item Add reference to the Liskhov principle of safe-substitution when stating that the system contract is a sound abstraction of the implementation.
  \item Add back in a few sentences on the contract for the filter since those have been removed with the addition of the formal definitions.
\end{compactitem}

\section{AGREE semantics for component synthesis}
\label{sec:semantics}
\input{semantics}

>>>>

\section{Compositional reasoning}
\label{sec:agree}
\input{agree}

\subsection{Revisions}
\begin{compactitem}
  \item \sout{Add in the AGREE specification for the system}
  \item \sout{Add in the AGREE verification conditions (e.g., similar to those in the Scheduled Components NFM submission)}
  \item Add reference to the Liskov principle of safe-substitution when stating that the system contract is a sound abstraction of the implementation.
  \item Add back in a few sentences on the contract for the filter since those have been removed with the addition of the formal definitions.
\end{compactitem}

\section{Formal contracts for the example system}
\input{sw-contract}

\subsection{Code contracts for cyber components}
\input{high-assurance-contracts}

%% \section{Synthesis from code contracts}
%% \label{sec:semantics}
%% \input{semantics}

### 2022-03-23 paper/synthesis.tex
checkpointing. Re-org is done (for now). Mostly done describing AGREE contracts. Synthesis.tex merged with semantics.tex

@@

%% \emph{Need some discussion of filters and their step-wise properties
%%   in relation to their infinitary properties. Reference to Johannes'
%%   work.}

@@

% A \emph{system} is a collection of \emph{components}, \emph{connections}
% between components, a \emph{scheduler} to order execution, and a
% \emph{system environment} for primary inputs.

@@

\subsection{Component Behavior}

Intuitively, for monitor specification $s$, \konst{stepFn} is the
concrete embodiment of $\konst{SynthEval}\;s$, as defined in Section
\ref{agree-semantics}. Its correctness amounts to showing that, given
a sequence of inputs, and an initial state meeting the initialization
constraints, iterating \konst{stepFn} produces a $\pi$ s.t. $\pi \in
\Lang{s}$; and taking the union over all input sequences and
initial states produces $\Lang{s}$ itself.

>>>>

The semantics of Section \ref{agree-semantics} supports a formal
connection between the original contract (and verification results of
the AGREE model checker being run on it), and code generated from
specifications of leaf level cyber-components. It also provides the
root meaning at the base of a chain of translation steps moving from
AGREE specifications to CakeML executables.

The first step in the chain maps the contract to a code-focused
representation. Assume given code contract $(I,O,A,\mathit{Eqs} \cup G \cup
P,\emptyset)$, environment $E$, and time $t$. The evaluation of $\mathit{Eqs}$
followed by the evaluation of $G$ results in a new environment $E'$
where the stream values for state variables and outputs have been
computed for time $t$. The step from $E$ to $E'$ is one full cycle in
the repeated evaluation of the component.

\begin{definition}[Evaluation]
We overload existing notation and write the evaluation of
$\mathit{Eqs}$ and then $G$ in environment $E$ at time $t$ as
$\sem{\mathit{Eqs}\cdot G}^E_t$. Each $v = e \in {\Eqs}$ is treated as
an environment transformation
\[
 \sem{v = e}^E_t = E[v(t) \mapsto\sem{e}^E_t] \ .
\]
modifying $E$ so that stream $v$ has value $\sem{e}^E_t$ at time $t$.
{\Eqs} is evaluated by folding the transformation left-to-right
through it. The transformation is also applied to the list of output
guarantees $G$, computing the values on output ports. The details are
omitted, being a bit messy because of the different kinds of output
ports available.
\end{definition}

\begin{definition}[Code contract correctness]
Assume code contract $(I,O,A,\mathit{Eqs} \cup G \cup P,\emptyset)$.
The contract is \emph{correct}, if for all $E$ and $t$, whenever the
assumptions (historically) hold in $E$ and evaluation steps from $E$
to $E'$, then the guarantees hold in $E'$:
\[
\sem{\konst{Hist}(A)}^E_t \land E' = \sem{\mathit{Eqs} \cdot G}^E_t \imp \sem{P}^{E'}_t
\]
\end{definition}
\footnote
{KLS: At this point we would like to assert that the AGREE ``consistency
 check'' for a contract implies code contract correctness.}

How does this notion of correctness integrate with the verification
conditions addressed by model checking? In \emph{contract
correctness}, the model checker is proving the following property
\[
\konst{Hist}(A) \imp P
\]
and in \emph{code contract correctness} we essentially prove a Hoare
triple of the form
\[
\set{\konst{Hist}(A)}\; (\mathit{Eqs} \cdot G) \; \set{P}
\]
This accords with intution, namely that AGREE is a kind of
`program-free program logic'; by pulling out a program $(\mathit{Eqs}
\cdot G)$ from a code contract we find ourselves in the tepid
bathwater of imperative program verification. In order to use the code
contract result in system contract verifcation conditions, one has to
show that the code contract result implies the system verification
condtion.

\subsubsection*{Wellformedness}
The evaluation semantics given above is based on the stream
computation model, where values `deep in the past' can be accessed in
computations. However, the conventional program languages we target
target do not support such a view. Thus code generation is only
defined for a class of \emph{wellformed} equations.

\begin{definition}[Wellformedness]
\end{definition}

\emph{Discussion on mapping program from stream environment to logic function
and then to CakeML}

@@

@@

@@

%% \subsection{Component Behavior}

%% Intuitively, for monitor specification $s$, \konst{stepFn} is the
%% concrete embodiment of $\konst{SynthEval}\;s$, as defined in Section
%% \ref{agree-semantics}. Its correctness amounts to showing that, given
%% a sequence of inputs, and an initial state meeting the initialization
%% constraints, iterating \konst{stepFn} produces a $\pi$ s.t. $\pi \in
%% \Lang{s}$; and taking the union over all input sequences and
%% initial states produces $\Lang{s}$ itself.

### 2022-03-23 paper/verification-conditions.tex
checkpointing. Re-org is done (for now). Mostly done describing AGREE contracts. Synthesis.tex merged with semantics.tex

AGREE generates, and then proves or disproves with model checking, a set of verification conditions to show that a system's component implementation is correct~\cite{agree2013}.
The verification conditions are formalized in \emph{past-time linear temporal logic} (PLTL).
PLTL is a first-order predicate calculus with temporal operators to reason about the truth values of formulas through time.
Its semantics are defined relative to a finite trace of system states $\pi = s_0, s_1, \ldots$, and a moment of evaluation in the trace, $i$.

The two PLTL operators necessary for the AGREE generated verification conditions are $\globally$ (globally) that looks forward in time along the trace and $\historically$ (historically) that looks backward in time along the trace.
These are defined as
\begin{eqnarray*}
 (\pi, i) \models \globally(f) & \iff & \forall j \ge i, (\pi, j) \models f \\
(\pi, i) \models \historically(f) & \iff & \forall 0 \le j \le i, (\pi, j) \models f
\end{eqnarray*}
The $\models$-operator is read as \emph{satisfies}.
A trace at a moment in time satisfies $\globally(f)$ if and only if it satisfies $f$ in the current and all future states of $\pi$.
Globally is invariant from the current moment into the future and historically is invariant from the beginning of the trace to the current moment.

A \emph{system} $\system = (\inputs, \outputs, \assumes,
\guarantees)$, where $\inputs$ is the input set, $\outputs$ is the
output set, $\assumes$ is the set of assumptions, and $\guarantees$ is
the set of guarantees.  A system is composed of a set of
\emph{components}, $\components$, together with their
inter-connections.  A component $\component$ is, hierarchically, also
a system, and may be designated by its own tuple
$(\inputs_\component, \outputs_\component, \assumes_\component,
\guarantees_\component)$.  From the components and connections,
$\mathbb{I}_\component$ is defined to be the set of components
providing input to some component $\component$ in the system, and
$\mathbb{O}$ is defined to be the set of components that provide the
output for the system.  A system $S$ is \emph{correct} if and only if for all
components $c \in C$:
\begin{equation}
            \globally(\historically(\assumes \wedge
            \bigwedge_{\component^\prime \in \mathbb{I}_\component} P_{\component^\prime})
            \implies \assumes_\component)
\end{equation}
\begin{equation}
            \globally(\historically(\assumes \wedge
            \bigwedge_{\component^\prime \in \mathbb{O}} \guarantees_{\component^\prime})
            \implies \guarantees)
\end{equation}
Condition (1) verifies the input assumptions on each component under
the system assumptions and upstream component guarantees.  It checks
if the component guarantees and system assumptions are strong enough
to imply input assumptions on all immediate downstream components.
Condition (2) checks the output guarantees of the system under the
system assumptions and component guarantees that provide the output.
It checks if the guarantees on components providing primary outputs
are strong enough to imply the system guarantees.

AGREE uses $k$-inductive model checking to prove or disprove each
generated verification condition.  If all the verification conditions
hold, then the system is said to be \emph{correct}, meaning that the
system composition meets input assumptions at each input as well as
the guarantees on the system output. A consequence of this result is
that $\globally(\historically(\assumes) \implies \guarantees)$ holds
for the system contract. As such, the system contract is a sound
abstraction of the system implementation.

The expanded property lists in \figref{fig:example-certificate} and
\figref{fig:hardened-certificate} are the results from verifying or
disproving the above verification conditions.  The additional
unexpanded results at the bottom of the figures prove
\emph{self-consistency} in the contracts.  It is not uncommon to
accidentally write contracts that are self-contradicting.  For
example, a contract may guarantee an output be two different values in
the same moment of time.  AGREE generates additional verification
conditions that prove each component contract, and the composition of
contracts, self-consistent.\footnote{KLS:Is this the same as
satisfiable?}

@@

The syntax of AGREE is essentially that of quantifier-free first order
logic (FOL) supplemented with a few temporal operators. The terms
(\emph{e}) are arithmetic expressions built from variables ($v$) and
numeric and boolean literals ($c$), while formulas (\emph{b}) are
built using logical connectives from atomic formulas (\emph{a}) based
on the familiar comparison operators.
\[
\begin{array}{rcl}
e & ::= & v \mid c \mid e \;\set{+,*,/}\; e \\
a & ::= & e\; \set{=,<}\; e \\
b & ::= & v \mid c \mid a \mid \neg b
            \mid b \; \set{\land,\lor,\imp,\iff}\; b
\end{array}
\]

There is also a conditional, $\itelse{b}{(-)}{(-)}$, for both terms
and formulas. Lastly, there are temporal operators $\konst{pre}(-)$,
delay $(-) \to (-)$, and $\konst{Hist}(-)$.

The semantics of terms and formulas is in terms of \emph{streams of
values}. Values encompass at least booleans and numbers, but can be
readily extended to include records and arrays. A value stream is a
total function from time (natural numbers) to values:
\[
 \konst{stream} = \mathbb{N} \to \konst{value}
\]
Given an \emph{environment} $E : \konst{name} \mapsto \konst{stream}$
binding variable names to value streams, the semantics $\sem{-}^E_t$
of terms and formulas, omitting the temporal operators, is
conventional. The value of a variable $v$ at time $t$ is found by
looking up the stream bound to $v$ in $E$ (call it $s$) and extracting
the value of $s$ at time $t$.

\[
\begin{array}{rcl}
\sem{v}^E_t & = & E(v)(t) \\
\sem{c}^E_t & = & c \\
\sem{e_1 + e_2}^E_t & = & \sem{e_1}^E_t + \sem{e_2}^E_t \\
   & \cdots & \\
\sem{b_1 \land b_2}^E_t & = & \sem{b_1}^E_t \land \sem{b_2}^E_t \\
   & \cdots & \\
\end{array}
\]

@@

\subsection{Code contracts}

Generally, AGREE specifications do not describe the computation
that a component performs. This is entirely by design: AGREE is
intended to reason about component behavior solely at the
specification level. However, the syntax of AGREE specifications
provides enough expressiveness to support the notion of a
\emph{code contract}: a component contract from which an implementation
can be extracted.

@@

\begin{definition}[Code contract]
A component of the form $(I_c,O_c,A_c,P_c)$ is a \emph{code contract}
if $\mathit{Eqs} \cup G \subseteq P_c$, where
\[\mathit{Eqs} = \set{v_1 = e_1, \cdots , v_n = e_n} \] is a non-empty set
of \konst{eq} statements and $G$ is the set of output guarantees, one for
each element of $O_c$. In the interpretation as code, the order of
elements of $\mathit{Eqs}$ is important, and is simply taken to be the
occurrence order of the \konst{eq} statements in the syntax. Thus we
will work with the
\emph{list} of equations $\mathit{Eqs} = [v_1 = e_1; \cdots ; v_n = e_n]$.
\end{definition}

>>>>

The AGREE specification language is based on stream concepts, and
operators, from the Lustre language \cite{10.1145/41625.41641}. Thus
the setting is synchronous dataflow where the inputs and outputs of
components are streams, and contracts express relationships between
input and output streams. When considering a system of components,
data flows through the components in dependency order, with inputs
being propagated to outputs through all contracts until they stabilize
(can't propagate further). Therefore, the subcomponent contracts, and
thus the top-level model, must be acyclic. (An apparent syntactic
cycle, where a component is linked back to itself, may be broken
temporally by inserting delay elements.)  Once the data propagation
has stabilized, the model proceeds to the next input data in the input
streams. The semantics do not model computation or communication
delay. The output of one contract is seen at the input of any
downstream contract in the same step of the input data stream.

From the system and component contracts, AGREE generates a set of
verification conditions to show that a system's component
implementation is correct~\cite{agree2013}.  The AGREE model checker
is then invoked to prove or disprove the verification
conditions. Contracts and verification conditions are expressed in
\emph{past-time linear temporal logic} (PLTL).\footnote{KLS: citation
needed.}  PLTL is a logic enhanced with temporal operators able to
reason about the truth values of formulas through time.  Its semantics
are defined relative to a point in time $i$ and a finite trace of
system states $\pi = s_0, s_1, \ldots, s_i$.

The two PLTL operators necessary for the AGREE generated verification
conditions are $\globally$ (globally) that looks forward in time along
the trace and $\historically$ (historically) that looks backward in
time along the trace.  These are defined as
\begin{eqnarray*}
 (\pi, i) \models \globally(f) & \iff & \forall j \ge i, (\pi, j) \models f \\
(\pi, i) \models \historically(f) & \iff & \forall 0 \le j \le i, (\pi, j) \models f
\end{eqnarray*}
The $\models$-operator is read as \emph{satisfies}.  A trace at a
moment in time satisfies $\globally(f)$ if and only if it satisfies
$f$ in the current and all future states of $\pi$.  $\globally(f)$ is
invariant from the current moment into the future and $\historically$ is
invariant from the beginning of the trace to the current moment.

A \emph{system} $\system = (\inputs, \outputs, \assumes,
\guarantees,C)$, where $\inputs$ is the input set, $\outputs$ is the
output set, $\assumes$ is the set of assumptions, $\guarantees$ is the
set of guarantees, and $C$ are subcomponents.  A subcomponent
$\component$ is, hierarchically, also a system, and may be designated
by its own tuple $(\inputs_\component, \outputs_\component,
\assumes_\component, \guarantees_\component, C_c)$.  From the
components and their connections, $\mathbb{I}_\component$ is defined
to be the set of components providing input to some component
$\component$ in the system, and $\mathbb{O}$ is defined to be the set
of components that provide the output for the system.  A system $S$ is
\emph{correct} if and only if for all components $c \in C$ the
following two verification conditions hold:
\begin{equation}
            \globally(\historically(\assumes \wedge
            \bigwedge_{\component^\prime \in \mathbb{I}_\component} P_{\component^\prime})
            \implies \assumes_\component)
\end{equation}
\begin{equation}
            \globally(\historically(\assumes \wedge
            \bigwedge_{\component^\prime \in \mathbb{O}} \guarantees_{\component^\prime})
            \implies \guarantees)
\end{equation}
Condition (1) verifies the input assumptions on each component under
the system assumptions and upstream component guarantees.  It checks
if the component guarantees and system assumptions are strong enough
to imply input assumptions on all immediate downstream components.
Condition (2) checks the output guarantees of the system under the
system assumptions and component guarantees that provide the output.
It checks if the guarantees on components providing primary outputs
are strong enough to imply the system guarantees.

If all the verification conditions hold (AGREE uses $k$-inductive
model checking to automatically prove or disprove each generated
verification condition), then the system is said to be \emph{correct},
meaning that the system composition meets input assumptions at each
input as well as the guarantees on the system output. A consequence of
this result is that $\globally(\historically(\assumes) \implies
\guarantees)$ holds for the system contract.

The expanded property lists in \figref{fig:example-certificate} and
\figref{fig:hardened-certificate} are the results from verifying or
disproving the above verification conditions.  The additional
unexpanded results at the bottom of the figures prove
\emph{self-consistency} in the contracts.  It is not uncommon to
accidentally write contracts that are self-contradicting.  For
example, a contract may guarantee an output be two different values in
the same moment of time.  AGREE generates additional verification
conditions that prove each component contract, and the composition of
contracts, self-consistent.

@@

We now give an overview of a formal model for AGREE. This provides a
setting in which we are able to relate the contract correctness
results discussed above, obtained via model-checking, with the code
generated from high-assurance contracts.  The syntax of AGREE is
essentially that of quantifier-free first order predicate logic
supplemented with a few temporal operators. The terms (\emph{e}) are
arithmetic expressions built from variables ($v$) and numeric and
boolean literals ($c$), while formulas (\emph{b}) are built using
logical connectives from atomic formulas (\emph{a}) based on the
familiar comparison operators.
\[
\begin{array}{rcl}
e & ::= & v \mid c \mid e \;\set{+,*,/}\; e \\
a & ::= & e\; \set{=,<}\; e \\
b & ::= & v \mid c \mid a \mid \neg b
            \mid b \; \set{\land,\lor,\imp,\iff}\; b
\end{array}
\]

There is also a conditional, $\itelse{b}{(-)}{(-)}$, for both terms
and formulas. Lastly, there are temporal operators $\konst{pre}(-)$,
\emph{delay} $(-) \to (-)$, and $\konst{Hist}(-)$.

The semantics of terms and formulas is in terms of \emph{streams of
values}. Values encompass at least booleans and numbers, but can be
readily extended to include records and arrays. A value stream is a
total function from time (natural numbers) to values:
\[
 \konst{stream} = \mathbb{N} \to \konst{value}
\]
Given an \emph{environment} $E : \konst{name} \mapsto \konst{stream}$
binding variable names to value streams, the semantics $\sem{-}^E_t$
of terms and formulas defines the meaning of compound syntax in terms
of the meaning of subexpressions. The value of a variable $v$ at time
$t$ is found by looking up the stream bound to $v$ in $E$ (call it
$s$) and returning $s_t$. Some clauses of the semantics follow,
omitting the temporal operators:
\[
\begin{array}{rcl}
\sem{v}^E_t & = & E(v)(t) \\
\sem{c}^E_t & = & c \\
\sem{e_1 + e_2}^E_t & = & \sem{e_1}^E_t + \sem{e_2}^E_t \\
   & \cdots & \\
\sem{b_1 \land b_2}^E_t & = & \sem{b_1}^E_t \land \sem{b_2}^E_t \\
   & \cdots & \\
\end{array}
\]

@@

\subsection{Code contracts}
\label{code-contracts}

Generally, AGREE specifications do not describe the computation that a
component performs. This is entirely by design: AGREE is intended to
reason about component behavior solely at the specification
level. However, the syntax of AGREE specifications provides enough
expressiveness to support the notion of a \emph{code contract}: a
contract from which an implementation can be extracted. First we must
discuss a class of guarantees---\emph{output guarantees}---which
determine the values on all output ports of a component.

@@

Informally, a code contract treats its \konst{eq} ``statements'' as
defining a list of assignments to state variables, and its output
guarantees as directives for producing output.

\begin{definition}[Code contract] A
  leaf component of the form $(I,O,A,P,\emptyset)$ is a
  \emph{code contract} if $\mathit{Eqs} \cup G \subseteq P$, where
\[\mathit{Eqs} = \set{v_1 = e_1, \cdots , v_n = e_n} \] is a non-empty set
of \konst{eq} statements and $G$ is the set of output guarantees, one for
each element of $O$. In the interpretation as code, the order of
elements of $\mathit{Eqs}$ is important, and is simply taken to be the
occurrence order of the \konst{eq} statements in the syntax. Thus we
will work with the
\emph{list} of equations $\mathit{Eqs} = [v_1 = e_1; \cdots ; v_n = e_n]$.
\end{definition}
